The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2025-02-21 index.qmd
added back notebook links, cleaned up _quarto.yml, and added figures back to the main doc

notebook-links: false
number-sections: false
citation:
  container-title: Unpublished
# date: last-modified
bibliography: Gavin_Thesis_Ref.bib
csl: nature.csl

@@

The manuscript was written in a 'reproducible manner'. The entire manuscript, including statistics reported, figures, and tables, can be reproduced here: [https://github.com/WeberLab/Chisep_CSVO2_Manuscript](https://github.com/WeberLab/Chisep_CSVO2_Manuscript)

>>>>

number-sections: false
citation:
  container-title: Pediatric Research
  volume: 97
  issue: 2
  doi: "not yet assigned"
# date: last-modified
bibliography: Gavin_Thesis_Ref.bib
csl: nature.csl

@@

The manuscript was written in a 'reproducible manner'. The entire manuscript, including statistics reported, figures, and tables, can be reproduced here: [weberlab.github.io/Chisep_CSVO2_Manuscript](https://weberlab.github.io/Chisep_CSVO2_Manuscript)
